### 2022-02-10 appendix_dg_toy/appendix.tex
.

%!TEX root = ../thesis.tex
\chapter{DG applied to a toy example}\label{appendix:example}
\begin{center}
    \begin{minipage}{0.8\textwidth}
        \textit{This appendix has been taken from Appendix~2 of \cite{blnos2022} with only minor changes, such as notations, so that this chapter is consistent with the rest of the thesis. I am a co-author of the paper \cite{blnos2022}. The conceptualisation of \cite{blnos2022} was originally by Vikram Sunkara, Nigel Bean and Giang Nguyen, and the original coding was done by Vikram Sunkara. I made significant contributions to Section~3 of the paper, expressing the operator-theoretic expressions to use the same partition as the approximation scheme. I contributed Sections~4.4 and 5.1. I extended the numerical experiments in Section~6 to higher orders and made all the plots in Section~6. Appendix~A is also my original work. I did a significant proportion of the writing of the manuscript and addressed the reviewers comments and also developed code for the numerical experiments.
        }
    \end{minipage}
    \end{center}
\renewcommand\thefigure{\arabic{figure}}
Here we include a small toy example to show how we construct a DG approximation and to help clarify the notation.

Consider a process \(\{(\overline X_t,Y_t,\varphi_t)\}_{t\geq 0}\) with two phases, \(\varphi_t\in\calS=\{1,2\}\) and generator matrix \(\bs T\). Let \(\mathcal I = 1.8\), and partition into two intervals \(\calD_1=[0,1]\) and \(\calD_2=[1,1.8]\), hence \(x_1=0,\,x_2=1,\,x_3=1.8\). We choose a basis of Lagrange polynomials of order 1 to define our approximation space. That is, 
\begin{align*}
	\phi_{1}^1(x) &= 1-x,& \phi_2^1(x) &= x, & &x \in\calD_1,\\
	\phi_{1}^2(x) &= \cfrac{1.8-x}{0.8},& \phi_2^2(x) &= \cfrac{x-1}{0.8}, & & x \in\calD_2.
\end{align*}
The mesh and basis functions are shown in Figure~\ref{fig: mesh}. 
\begin{figure}
\centering
\begin{tikzpicture}[scale=4]
    % Draw axes
    \draw [<->,thick] (0,1.1) node (yaxis) [above] {}
        |- (2,0) node (xaxis) [right] {$x$};
    % Draw two intersecting lines
    \draw[red] (0,0) coordinate (a_1) -- (1,1) coordinate (a_2);
    \draw[blue] (0,1) coordinate (b_1) -- (1,0) coordinate (b_2);
    \draw[red] (1,0) coordinate (a_3) -- (1.8,1) coordinate (a_4);
    \draw[blue] (1,1) coordinate (b_3) -- (1.8,0) coordinate (b_4);
    \draw[dashed] (1,0) coordinate (c_1) -- (1,1.1) coordinate (c_2);
    \draw[dashed] (1.8,0) coordinate (d_1) -- (1.8,1.1) coordinate (d_2);
    \filldraw (0.5,0) circle (0pt) node[align=center, below] {\(\calD_1\)};
    \filldraw (1.4,0) circle (0pt) node[align=center, below] {\(\calD_2\)};
    \filldraw (0,0) circle (0pt) node[align=center, below] {\(x_1=0\)};
    \filldraw (1,0) circle (0pt) node[align=center, below] {\(x_2=1\)};
    \filldraw (1.8,0) circle (0pt) node[align=center, below] {\(x_3=1.8\)};  
    \filldraw (0,1) circle (0pt) node[align=center, left] {\(1\)};    
    \filldraw (0,1) circle (0pt) node[align=center, right] {\color{blue}\(\phi_1^1(x)\)};    
    \filldraw (1,1) circle (0pt) node[align=center, left] {\color{red}\(\phi_2^1(x)\)};    
    \filldraw (1,1) circle (0pt) node[align=center, right] {\color{blue}\(\phi_1^2(x)\)};    
    \filldraw (1.8,1) circle (0pt) node[align=center, left] {\color{red}\(\phi_2^2(x)\)};    
\end{tikzpicture}
\caption{A mesh with nodes \(x_1=0\), \(x_2=1\) and \(x_3=1.8\) and cells \(\calD_1=[0,1]\), \(\calD_2=[1,1.8]\). There are two basis functions on each cell. Point masses are located at \(x_1=0\) and \(x_3=1.8\).\label{fig: mesh}}
\end{figure}
We can verify that the matrices \(\bs M\) and \(\bs G\) are given by 
\[\bs M = \left[\begin{array}{cc|cc} 1/3 & 1/6 & 0 & 0 \\ 1/6 & 1/3 & 0 & 0 \\\hline 0 & 0 & 4/15 & 4/30 \\ 0 & 0 & 4/30 & 4/15 \end{array}\right],\, \bs G = \left[\begin{array}{cc|cc} -1/2 & 1/2 & 0 & 0 \\ -1/2 & 1/2 & 0 & 0 \\\hline 0 & 0 & -1/2 & 1/2 \\ 0 & 0 & -1/2 & 1/2 \end{array}\right].\] 
The matrix \(\bs P\) is given by 
\[\bs P = \left[\begin{array}{cc|cc} 1/2 & 0 & 0 & 0 \\ 0 & 1/2 & 0 & 0 \\\hline 0 & 0 & 2/5 & 0 \\ 0 & 0 & 0 & 2/5 \end{array}\right].\]

@@

Suppose that \(r_1(x)>0\) on \(\calD_1=\mathcal F_1^+\) and \(r_1(x)<0\) on \(\calD_2\cup\{1\}=\mathcal F_1^-\), and further, that \(r_2(x)<0\) on \(\{0\}\cup\calD_1=\mathcal F_2^-\) and \(r_2(x)>0\) on \(\calD_2=\mathcal F_2^+\). Specifically, let 
\[r_1(x) = \begin{cases} 1 & x \in [0,1], \\ -1 & x \in [1,1.8],\end{cases}\quad r_2(x) = \begin{cases} -1 & x = 0, \\ -2 & x \in (0,1], \\ 1 & x \in [1,1.8]. \end{cases}\]

@@

Then, constructing \({  \bs B}\) we get 
\[
\begin{blockarray}{c|cc|cc|cc|cc|c}
\nabla & \BAmulticolumn{4}{c|}{\calD_1} & \BAmulticolumn{4}{c|}{\calD_2} & \Delta\\
\calF_2^- & \BAmulticolumn{2}{c|}{\calF_1^+} & \BAmulticolumn{2}{c|}{\calF_2^-} & \BAmulticolumn{2}{c|}{\calF_1^-} & \BAmulticolumn{2}{c|}{\calF_2^+} & \calF_1^-\\
q_{\nabla,1} & a_{1,1}^1 & a_{1,2}^1 & a_{2,1}^1 & a_{2,2}^1 & a_{1,1}^2 & a_{1,2}^2 & a_{2,1}^2 & a_{2,2}^2 & q_{\Delta,1}\\\BAhline
\begin{block}{[c|cc|cc|cc|cc|c]} 
T_{22} & 4T_{21} & -2T_{21} & 0 & 0 & 0 & 0 & 0 & 0 & 0\\\BAhline
0 & T_{11}-3 & 3 & T_{12} & 0 & 0 & 0 & 0 & 0 & 0 \\
0 & -1 & T_{11}-1 & 0 & T_{12} & 5 & -2.5 & 0 & 0 & 0 \\\BAhline 
2 & T_{21} & 0 & T_{22}-2 & -2 & 0 & 0 & 0 & 0 & 0 \\ 
0 & 0 & T_{21} & 6 & T_{22}-6 & 0 & 0 & 0 & 0 & 0\\\BAhline
0 & 0 & 0 & 0 & 0 & T_{11}-\frac{15}{4} & \frac{15}{4} & T_{12} & 0 & 0 \\ 
0 & 0 & 0 & 0 & 0 & -\frac{5}{4} & T_{11}-\frac{5}{4} & 0 & T_{12} &1\\\BAhline
0 & 0 & 0 & -4 & 8 & T_{21} & 0 & T_{22}-\frac{5}{2} & -\frac{5}{2} & 0 \\
0 & 0 & 0 & 0 & 0 & 0 & T_{21} & \frac{15}{2} & T_{22}-\frac{15}{2} & 0 \\\BAhline
0 & 0 & 0 & 0 & 0 & 0 & 0 & -2T_{12} & 4T_{12} & T_{11} \\
\end{block}
\end{blockarray}.
%\\&{}+\left[\begin{array}{c|cc|cc|cc|cc|c} 
%0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\\hline 
%0 & -3 & 3 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
%0 & -1 & -1 & 0 & 0 & 4 & -2 & 0 & 0 & 0 \\\hline 
%4 & 0 & 0 & -2 & -2 & 0 & 0 & 0 & 0 & 0 \\ 
%0 & 0 & 0 & 6 & -6 & 0 & 0 & 0 & 0 & 0 \\\hline
%0 & 0 & 0 & 0 & 0 & -3.75 & 3.75 & 0 & 0 & 0 \\
%0 & 0 & 0 & 0 & 0 & -1.25 & -1.25 & 0 & 0 & 2.5 \\\hline
%0 & 0 & 0 & -5 & 10 & 0 & 0 & -2.5 & -2.5 & 0 \\
%0 & 0 & 0 & 0 & 0 & 0 & 0 & 7.5 & -7.5 & 0 \\\hline
%0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 
%\end{array}\right].
\]

@@

Now, to find \( {\bs\xi}\), we solve the linear system in Equations \eqref{eqn:xi1}-\eqref{eqn:xi2}. The result is a vector which we denote, 
\[ {\bs\xi} = \left[\begin{array}{c|cc|cc|c} {\xi}^\nabla_{2} &  {\xi}_{2,1}^1 &  {\xi}_{2,2}^1 &  {\xi}_{1,1}^2 &  {\xi}_{1,2}^2 &  {\xi}_{1}^\Delta \end{array}\right],\]
where \( {\xi}^\nabla_{2}\) is an approximation to \( \lim\limits_{n\to\infty}\mathbb{P}\left(\overline X_{\theta_n} =0, \varphi_{\theta_n} = 2\right)\) and \( {\xi}^\Delta_{1}\) is an approximation to the artificial point mass \( \lim\limits_{n\to\infty}\mathbb{P}\left(\overline X_{\theta_n} =1.8, \varphi_{\theta_n} = 1\right)\). For \(x\in\calD_1\) an approximation to the density of \( \lim\limits_{n\to\infty}\mathbb{P}\left(\overline X_{\theta_n} \in \wrt x, \varphi_{\theta_n} = 2\right)\), is constructed as \( {\xi}_{2,1}^1\phi_1^1(x) +  {\xi}_{2,2}^1\phi_2^1(x)\). For \(x\in\calD_2\) an approximation to the density of \( \lim\limits_{n\to\infty}\mathbb{P}\left(\overline X_{\theta_n} \in \wrt x, \varphi_{\theta_n} = 1\right)\), is constructed as \( {\xi}_{1,1}^2\phi_1^2(x) +  {\xi}_{1,2}^2\phi_2^2(x).\)

@@

For the point masses we have 
\[ {\bs p}^- = \left[\begin{array}{c|cc|cc|c} {p}_{2}^\nabla &  {p}_{2,1}^1 &  {p}_{2,2}^1 &  {p}_{1,1}^2 &  {p}_{1,2}^2 &  {p}_{1}^\Delta \end{array}\right],\]
where \( {p}_{2}^\nabla\) is an approximation to \( \lim\limits_{t\to\infty}\mathbb{P}\left(\overline X_{t} =0, Y_t=0, \varphi_{t} = 2\right)\) and \( {p}_{1}^\Delta\) is an approximation to the artificial point mass \( \lim\limits_{t\to\infty}\mathbb{P}\left(\overline X_t =1.8, Y_t=0, \varphi_{t} = 1\right)\). For \(x\in\calD_1\), an approximation to the density of \( \lim\limits_{t\to\infty}\mathbb{P}\left(\overline X_t \in \wrt x, Y_t = 0, \varphi_{t} = 2\right)\), is constructed as \( {p}_{2,1}^1\phi_1^1(x) +  {p}_{2,2}^1\phi_2^1(x)\). For \(x\in\calD_2\), an approximation to the density of \( \lim\limits_{t\to\infty}\mathbb{P}\left(\overline X_t \in \wrt x, Y_t = 0, \varphi_{t} = 1\right)\), is constructed as \( {p}_{1,1}^2\phi_1^2(x) +  {p}_{1,2}^2\phi_2^2(x).\)

Similarly, for \( {\bs\pi}^-(y)\), we have 
\[ {\bs \pi}^-(y) = \left[\begin{array}{c|cc|cc|c} {\pi}_{2}^\nabla(y) &  {\pi}_{2,1}^1(y) &  {\pi}_{2,2}^1(y) &  {\pi}_{1,1}^2(y) &  {\pi}_{1,2}^2(y) &  {\pi}_{1}^\Delta(y) \end{array}\right],\]
where \( {\pi}_{2}^\nabla(y)\) is an approximation to \( \lim\limits_{t\to\infty}\mathbb{P}\left(\overline X_t =0, Y_t\in\wrt y, \varphi_{t} = 2\right)\) and \( {\pi}_{1}^\Delta(y)\) is an approximation to the artificial point mass \( \lim\limits_{t\to\infty}\mathbb{P}\left(\overline X_t =1.8, Y_t\in \wrt y, \varphi_{t} = 1\right)\). For \(x\in\calD_1\) an approximation to the density of \( \lim\limits_{t\to\infty}\mathbb{P}\left(\overline X_t \in \wrt x, Y_t \in \wrt y, \varphi_{t} = 2\right)\), is constructed as \( {\pi}_{2,1}^1(y)\phi_1^1(x) +  {\pi}_{2,2}^1(y)\phi_2^1(x)\). For \(x\in\calD_2\) an approximation to the density of \( \lim\limits_{t\to\infty}\mathbb{P}\left(\overline X_t \in \wrt x, Y_t \in \wrt y, \varphi_{t} = 1\right)\), is constructed as \( {\pi}_{1,1}^2(y)\phi_1^2(x) +  {\pi}_{1,2}^2(y)\phi_2^2(x).\)

For \( {\bs\pi}^+(y)\), we have 
\[ {\bs \pi}^+(y) = \left[\begin{array}{cc|cc}  {\pi}_{1,1}^1(y) &  {\pi}_{1,2}^1(y) &  {\pi}_{2,1}^2(y) &  {\pi}_{2,2}^2(y) \end{array}\right].\]
For \(x\in\calD_1\) an approximation to the joint density of \( \lim\limits_{t\to\infty}\mathbb{P}\left(\overline X_t \in \wrt x, Y_t \in \wrt y, \varphi_{t} = 1\right)\) is constructed as \( {\pi}_{1,1}^1(y)\phi_1^1(x) +  {\pi}_{1,2}^1(y)\phi_2^1(x)\). For \(x\in\calD_2\) an approximation to the density of \( \lim\limits_{t\to\infty}\mathbb{P}\left(\overline X_t \in \wrt x, Y_t \in \wrt y, \varphi_{t} = 2\right)\) is constructed as \( {\pi}_{2,1}^2(y)\phi_1^2(x) +  {\pi}_{2,2}^2(y)\phi_2^2(x).\)

In summary, for \(i\in\calS\), a global approximation of the joint stationary distribution is
\begin{align*}
	\lim\limits_{t\to\infty}\mathbb{P}\left(\overline X_t \in \wrt x, Y_t \in \wrt y, \varphi_{t} = i\right) &\approx \displaystyle \sum_{r\in\{1,2\},k\in\{1,2\}}  {\pi}_{i,r}^k(y)\phi_r^k(x)\wrt x \wrt y ,\quad x\in(0,1.8),\, y>0, \\
	\lim\limits_{t\to\infty}\mathbb{P}\left(\overline X_t \in \wrt x, Y_t=0, \varphi_{t} = i\right) & \approx \displaystyle \sum_{r\in\{1,2\},k\in\{1,2\}}  {p}_{i,r}^k\phi_r^k(x)\wrt x ,\quad x\in(0,1.8),\\
	 \lim\limits_{t\to\infty}\mathbb{P}\left(\overline X_t =0, Y_t \in \wrt y, \varphi_{t} = i\right) & \approx{\pi}_{i}^\nabla(y)\wrt y,\quad y>0, \\
	 \lim\limits_{t\to\infty}\mathbb{P}\left(\overline X_t = 0, Y_t =0, \varphi_{t} = i\right) & \approx {p}_{i}^\nabla,\quad \\ 
	 \lim\limits_{t\to\infty}\mathbb{P}\left(\overline X_t = 1.8, Y_t \in \wrt y, \varphi_{t} = i\right) & \approx {\pi}_{i}^\Delta(y)\wrt y,\quad y>0, \\
	 \lim\limits_{t\to\infty}\mathbb{P}\left(\overline X_t = 1.8, Y_t = 0, \varphi_{t} = i\right) & \approx {p}_{i}^\Delta.\quad
\end{align*}
%\[\left[\begin{array}{c|cc|cc|cc|cc|c} {\pi}_{2,\nabla}(y) &  {\pi}_{1,1}^1(y) &  {\pi}_{1,2}^1(y) &  {\pi}_{2,1}^1(y) &  {\pi}_{2,2}^1(y) &  {\pi}_{1,1}^2(y) &  {\pi}_{1,2}^2(y) &  {\pi}_{2,1}^2(y) &  {\pi}_{2,2}^2(y) &  {\pi}_{1,\Delta}(y) \end{array}\right]\]

>>>>

%!TEX root = ../thesis.tex
\chapter{DG applied to a toy example}\label{appendix:example}
\begin{center}
    \begin{minipage}{0.8\textwidth}
        \textit{This appendix has been taken from Appendix~2 of \cite{blnos2022} with only minor changes, such as notations, so that this chapter is consistent with the rest of the thesis. I am a co-author of the paper \cite{blnos2022}.
        }
    \end{minipage}
    \end{center}
\renewcommand\thefigure{\arabic{figure}}
Here we include a small toy example to show how we construct a DG approximation and to help clarify the notation.

Consider a process \(\{(\overline X_t,Y_t,\varphi_t)\}_{t\geq 0}\) with two phases, \(\varphi_t\in\calS=\{1,2\}\) and generator matrix \(\bs T\). Let \(\mathcal I = 1.8\), and partition into two intervals \(\calD_0=[0,1]\) and \(\calD_1=[1,1.8]\), hence \(x_0=0,\,x_1=1,\,x_2=1.8\). We choose a basis of Lagrange polynomials of order 1 to define our approximation space. That is, 
\begin{align*}
	\phi_{0}^1(x) &= 1-x,& \phi_0^2(x) &= x, & &x \in\calD_0,\\
	\phi_{1}^1(x) &= \cfrac{1.8-x}{0.8},& \phi_1^2(x) &= \cfrac{x-1}{0.8}, & & x \in\calD_1.
\end{align*}
The mesh and basis functions are shown in Figure~\ref{fig: mesh}. 
\begin{figure}
\centering
\begin{tikzpicture}[scale=4]
    % Draw axes
    \draw [<->,thick] (0,1.1) node (yaxis) [above] {}
        |- (2,0) node (xaxis) [right] {$x$};
    % Draw two intersecting lines
    \draw[red] (0,0) coordinate (a_1) -- (1,1) coordinate (a_2);
    \draw[blue] (0,1) coordinate (b_1) -- (1,0) coordinate (b_2);
    \draw[red] (1,0) coordinate (a_3) -- (1.8,1) coordinate (a_4);
    \draw[blue] (1,1) coordinate (b_3) -- (1.8,0) coordinate (b_4);
    \draw[dashed] (1,0) coordinate (c_1) -- (1,1.1) coordinate (c_2);
    \draw[dashed] (1.8,0) coordinate (d_1) -- (1.8,1.1) coordinate (d_2);
    \filldraw (0.5,0) circle (0pt) node[align=center, below] {\(\calD_0\)};
    \filldraw (1.4,0) circle (0pt) node[align=center, below] {\(\calD_1\)};
    \filldraw (0,0) circle (0pt) node[align=center, below] {\(x_0=0\)};
    \filldraw (1,0) circle (0pt) node[align=center, below] {\(x_1=1\)};
    \filldraw (1.8,0) circle (0pt) node[align=center, below] {\(x_2=1.8\)};  
    \filldraw (0,1) circle (0pt) node[align=center, left] {\(1\)};    
    \filldraw (0,1) circle (0pt) node[align=center, right] {\color{blue}\(\phi_0^1(x)\)};    
    \filldraw (1,1) circle (0pt) node[align=center, left] {\color{red}\(\phi_0^2(x)\)};    
    \filldraw (1,1) circle (0pt) node[align=center, right] {\color{blue}\(\phi_1^1(x)\)};    
    \filldraw (1.8,1) circle (0pt) node[align=center, left] {\color{red}\(\phi_1^2(x)\)};    
\end{tikzpicture}
\caption{A mesh with nodes \(x_0=0\), \(x_1=1\) and \(x_2=1.8\) and cells \(\calD_0=[0,1]\), \(\calD_1=[1,1.8]\). There are two basis functions on each cell. Point masses are located at \(x_0=0\) and \(x_2=1.8\).\label{fig: mesh}}
\end{figure}
We can verify that the matrices \(\bs M\) and \(\bs G\) are given by 
\[\bs M = \left[\begin{array}{cc|cc} 1/3 & 1/6 & 0 & 0 \\ 1/6 & 1/3 & 0 & 0 \\\hline 0 & 0 & 4/15 & 4/30 \\ 0 & 0 & 4/30 & 4/15 \end{array}\right],\, \bs G = \left[\begin{array}{cc|cc} -1/2 & 1/2 & 0 & 0 \\ -1/2 & 1/2 & 0 & 0 \\\hline 0 & 0 & -1/2 & 1/2 \\ 0 & 0 & -1/2 & 1/2 \end{array}\right].\] 
The matrix \(\bs P\) is given by 
\[\bs P = \left[\begin{array}{cc|cc} 1/2 & 0 & 0 & 0 \\ 0 & 1/2 & 0 & 0 \\\hline 0 & 0 & 2/5 & 0 \\ 0 & 0 & 0 & 2/5 \end{array}\right].\]

@@

Suppose that \(r_1(x)>0\) on \(\calD_0=\mathcal F_1^+\) and \(r_1(x)<0\) on \(\calD_1\cup\{1\}=\mathcal F_1^-\), and further, that \(r_2(x)<0\) on \(\{0\}\cup\calD_0=\mathcal F_2^-\) and \(r_2(x)>0\) on \(\calD_1=\mathcal F_2^+\). Specifically, let 
\[r_1(x) = \begin{cases} 1 & x \in [0,1], \\ -1 & x \in [1,1.8],\end{cases}\quad r_2(x) = \begin{cases} -1 & x = 0, \\ -2 & x \in (0,1], \\ 1 & x \in [1,1.8]. \end{cases}\]

@@

Then, constructing \({  \bs B}\) we get 
\[
\begin{blockarray}{c|cc|cc|cc|cc|c}
{-1} & \BAmulticolumn{4}{c|}{\calD_0} & \BAmulticolumn{4}{c|}{\calD_2} & {K+1}\\
\calF_2^- & \BAmulticolumn{2}{c|}{\calF_1^+} & \BAmulticolumn{2}{c|}{\calF_2^-} & \BAmulticolumn{2}{c|}{\calF_1^-} & \BAmulticolumn{2}{c|}{\calF_2^+} & \calF_1^-\\
q_{{-1},0} & a_{0,1}^1 & a_{0,1}^2 & a_{0,2}^1 & a_{0,2}^2 & a_{1,1}^1 & a_{1,1}^2 & a_{1,2}^1 & a_{1,2}^2 & q_{{K+1},1}\\\BAhline
\begin{block}{[c|cc|cc|cc|cc|c]} 
T_{22} & 4T_{21} & -2T_{21} & 0 & 0 & 0 & 0 & 0 & 0 & 0\\\BAhline
0 & T_{11}-3 & 3 & T_{12} & 0 & 0 & 0 & 0 & 0 & 0 \\
0 & -1 & T_{11}-1 & 0 & T_{12} & 5 & -2.5 & 0 & 0 & 0 \\\BAhline 
2 & T_{21} & 0 & T_{22}-2 & -2 & 0 & 0 & 0 & 0 & 0 \\ 
0 & 0 & T_{21} & 6 & T_{22}-6 & 0 & 0 & 0 & 0 & 0\\\BAhline
0 & 0 & 0 & 0 & 0 & T_{11}-\frac{15}{4} & \frac{15}{4} & T_{12} & 0 & 0 \\ 
0 & 0 & 0 & 0 & 0 & -\frac{5}{4} & T_{11}-\frac{5}{4} & 0 & T_{12} &1\\\BAhline
0 & 0 & 0 & -4 & 8 & T_{21} & 0 & T_{22}-\frac{5}{2} & -\frac{5}{2} & 0 \\
0 & 0 & 0 & 0 & 0 & 0 & T_{21} & \frac{15}{2} & T_{22}-\frac{15}{2} & 0 \\\BAhline
0 & 0 & 0 & 0 & 0 & 0 & 0 & -2T_{12} & 4T_{12} & T_{11} \\
\end{block}
\end{blockarray}.
%\\&{}+\left[\begin{array}{c|cc|cc|cc|cc|c} 
%0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\\hline 
%0 & -3 & 3 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
%0 & -1 & -1 & 0 & 0 & 4 & -2 & 0 & 0 & 0 \\\hline 
%4 & 0 & 0 & -2 & -2 & 0 & 0 & 0 & 0 & 0 \\ 
%0 & 0 & 0 & 6 & -6 & 0 & 0 & 0 & 0 & 0 \\\hline
%0 & 0 & 0 & 0 & 0 & -3.75 & 3.75 & 0 & 0 & 0 \\
%0 & 0 & 0 & 0 & 0 & -1.25 & -1.25 & 0 & 0 & 2.5 \\\hline
%0 & 0 & 0 & -5 & 10 & 0 & 0 & -2.5 & -2.5 & 0 \\
%0 & 0 & 0 & 0 & 0 & 0 & 0 & 7.5 & -7.5 & 0 \\\hline
%0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 
%\end{array}\right].
\]

@@

Now, to find \( {\bs\xi}\), we solve the linear system in Equations \eqref{eqn:xi1}-\eqref{eqn:xi2}. The result is a vector which we denote, 
\[ {\bs\xi} = \left[\begin{array}{c|cc|cc|c} {\xi}_{-1,2} &  {\xi}_{0,2}^1 &  {\xi}_{0,2}^2 &  {\xi}_{1,1}^1 &  {\xi}_{1,1}^2 &  {\xi}_{K+1,1} \end{array}\right],\]
where \( {\xi}_{-1,2}\) is an approximation to \( \lim\limits_{n\to\infty}\mathbb{P}\left(\overline X_{\theta_n} =0, \varphi_{\theta_n} = 2\right)\) and \( {\xi}_{K+1,1}\) is an approximation to the artificial point mass \( \lim\limits_{n\to\infty}\mathbb{P}\left(\overline X_{\theta_n} =1.8, \varphi_{\theta_n} = 1\right)\). For \(x\in\calD_0\) an approximation to the density of \( \lim\limits_{n\to\infty}\mathbb{P}\left(\overline X_{\theta_n} \in \wrt x, \varphi_{\theta_n} = 2\right)\), is constructed as \( {\xi}_{0,2}^0\phi_0^1(x) +  {\xi}_{0,2}^0\phi_0^1(x)\). For \(x\in\calD_1\) an approximation to the density of \( \lim\limits_{n\to\infty}\mathbb{P}\left(\overline X_{\theta_n} \in \wrt x, \varphi_{\theta_n} = 1\right)\), is constructed as \( {\xi}_{1,1}^1\phi_1^1(x) +  {\xi}_{1,1}^2\phi_1^2(x).\)

@@

For the point masses we have 
\[ {\bs p}^- = \left[\begin{array}{c|cc|cc|c} {p}_{-1,2} &  {p}_{0,2}^1 &  {p}_{0,2}^2 &  {p}_{1,1}^1 &  {p}_{1,1}^2 &  {p}_{K+1,1} \end{array}\right],\]
where \( {p}_{-1,2}\) is an approximation to \( \lim\limits_{t\to\infty}\mathbb{P}\left(\overline X_{t} =0, Y_t=0, \varphi_{t} = 2\right)\) and \( {p}_{K+1,1}\) is an approximation to the artificial point mass \( \lim\limits_{t\to\infty}\mathbb{P}\left(\overline X_t =1.8, Y_t=0, \varphi_{t} = 1\right)\). For \(x\in\calD_0\), an approximation to the density of \( \lim\limits_{t\to\infty}\mathbb{P}\left(\overline X_t \in \wrt x, Y_t = 0, \varphi_{t} = 2\right)\), is constructed as \( {p}_{0,2}^1\phi_0^1(x) +  {p}_{0,2}^2\phi_0^2(x)\). For \(x\in\calD_1\), an approximation to the density of \( \lim\limits_{t\to\infty}\mathbb{P}\left(\overline X_t \in \wrt x, Y_t = 0, \varphi_{t} = 1\right)\), is constructed as \( {p}_{1,1}^1\phi_1^1(x) +  {p}_{1,1}^2\phi_1^2(x).\)

Similarly, for \( {\bs\pi}^-(y)\), we have 
\[ {\bs \pi}^-(y) = \left[\begin{array}{c|cc|cc|c} {\pi}_{-1,2}(y) &  {\pi}_{0,2}^1(y) &  {\pi}_{0,2}^2(y) &  {\pi}_{1,1}^1(y) &  {\pi}_{1,1}^2(y) &  {\pi}_{K+1,1}(y) \end{array}\right],\]
where \( {\pi}_{-1,2}(y)\) is an approximation to \( \lim\limits_{t\to\infty}\mathbb{P}\left(\overline X_t =0, Y_t\in\wrt y, \varphi_{t} = 2\right)\) and \( {\pi}_{K+1,1}(y)\) is an approximation to the artificial point mass \( \lim\limits_{t\to\infty}\mathbb{P}\left(\overline X_t =1.8, Y_t\in \wrt y, \varphi_{t} = 1\right)\). For \(x\in\calD_0\) an approximation to the density of \( \lim\limits_{t\to\infty}\mathbb{P}\left(\overline X_t \in \wrt x, Y_t \in \wrt y, \varphi_{t} = 2\right)\), is constructed as \( {\pi}_{0,2}^1(y)\phi_0^1(x) +  {\pi}_{0,2}^2(y)\phi_0^2(x)\). For \(x\in\calD_1\) an approximation to the density of \( \lim\limits_{t\to\infty}\mathbb{P}\left(\overline X_t \in \wrt x, Y_t \in \wrt y, \varphi_{t} = 1\right)\), is constructed as \( {\pi}_{1,1}^1(y)\phi_1^1(x) +  {\pi}_{1,1}^2(y)\phi_1^2(x).\)

For \( {\bs\pi}^+(y)\), we have 
\[ {\bs \pi}^+(y) = \left[\begin{array}{cc|cc}  {\pi}_{0,1}^1(y) &  {\pi}_{0,1}^2(y) &  {\pi}_{1,2}^1(y) &  {\pi}_{1,2}^2(y) \end{array}\right].\]
For \(x\in\calD_0\) an approximation to the joint density of \( \lim\limits_{t\to\infty}\mathbb{P}\left(\overline X_t \in \wrt x, Y_t \in \wrt y, \varphi_{t} = 1\right)\) is constructed as \( {\pi}_{0,1}^1(y)\phi_0^1(x) +  {\pi}_{0,1}^2(y)\phi_0^2(x)\). For \(x\in\calD_1\) an approximation to the density of \( \lim\limits_{t\to\infty}\mathbb{P}\left(\overline X_t \in \wrt x, Y_t \in \wrt y, \varphi_{t} = 2\right)\) is constructed as \( {\pi}_{1,2}^1(y)\phi_1^1(x) +  {\pi}_{1,2}^2(y)\phi_1^2(x).\)

In summary, for \(i\in\calS\), a global approximation of the joint stationary distribution is
\begin{align*}
	\lim\limits_{t\to\infty}\mathbb{P}\left(\overline X_t \in \wrt x, Y_t \in \wrt y, \varphi_{t} = i\right) &\approx \displaystyle \sum_{r\in\{1,2\},k\in\{0,1\}}  {\pi}_{i,k}^r(y)\phi_k^r(x)\wrt x \wrt y ,\quad x\in(0,1.8),\, y>0, \\
	\lim\limits_{t\to\infty}\mathbb{P}\left(\overline X_t \in \wrt x, Y_t=0, \varphi_{t} = i\right) & \approx \displaystyle \sum_{r\in\{1,2\},k\in\{0,1\}}  {p}_{k,i}^r\phi_k^r(x)\wrt x ,\quad x\in(0,1.8),\\
	 \lim\limits_{t\to\infty}\mathbb{P}\left(\overline X_t =0, Y_t \in \wrt y, \varphi_{t} = i\right) & \approx{\pi}_{-1,i}(y)\wrt y,\quad y>0, \\
	 \lim\limits_{t\to\infty}\mathbb{P}\left(\overline X_t = 0, Y_t =0, \varphi_{t} = i\right) & \approx {p}_{-1,i},\quad \\ 
	 \lim\limits_{t\to\infty}\mathbb{P}\left(\overline X_t = 1.8, Y_t \in \wrt y, \varphi_{t} = i\right) & \approx {\pi}_{K+1,i}(y)\wrt y,\quad y>0, \\
	 \lim\limits_{t\to\infty}\mathbb{P}\left(\overline X_t = 1.8, Y_t = 0, \varphi_{t} = i\right) & \approx {p}_{K+1,i}.\quad
\end{align*}
%\[\left[\begin{array}{c|cc|cc|cc|cc|c} {\pi}_{2,{-1}}(y) &  {\pi}_{1,1}^1(y) &  {\pi}_{1,2}^1(y) &  {\pi}_{2,1}^1(y) &  {\pi}_{2,2}^1(y) &  {\pi}_{1,1}^2(y) &  {\pi}_{1,2}^2(y) &  {\pi}_{2,1}^2(y) &  {\pi}_{2,2}^2(y) &  {\pi}_{1,{K+1}}(y) \end{array}\right]\]
